\subsection{arcls}\label{sec:arcls}
The \texttt{arcls} \index{arcls}\index{commands:arcls} is a simple
utility that allows to list contents and view some attributes of
objects of a specified (by an URL) remote directory.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcls [options] $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-l} &  & detailed listing\\
    \texttt{-L} &  & detailed listing including URLs from which file can 
    be downloaded and\\ & & temporary cached locations\\
    Arguments:&&\\
    \texttt{URL} && file or directory URL\\
\end{longtable}

This tool is very convenient not only because it allows to list files
at a Storage Element or records in an indexing service, but also
because it can give a quick overview of a job's working directory,
which is explicitly given by job ID.

Usage examples can be as follows:

\begin{verbatim}
    ngls rls://rc.host:38203/logical_file_name
    ngls -l gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535
    ngls -L srm://grid.uio.no:58000/srm/managerv1/johndoe/log2
\end{verbatim}

Examples of URLs accepted by this tool can be found in
Section~\ref{sec:urls}, though \texttt{arcls} won't be able to list a
directory at an HTTP server, as they normally do not return directory
listings.

\subsection{arccp}\label{sec:arccp}

The \texttt{arccp}\footnote{In ARC $\leq$ 0.5.28 was called
  \texttt{ngcopy}} \index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the Grid Manager,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: from -3 = quiet to 3 = verbose\\
    \texttt{-y} & \textit{cache\_path} & path to local cache (use to put file into cache)\\
    \texttt{-Y} & \textit{cache\_data\_path} & path for cache data (if different from -y)\\
    \texttt{-p} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
    \texttt{-n} && do not try to force passive transfer\\
    \texttt{-i} && show progress indicator\\
    \texttt{-u} && use secure transfer (insecure by default)\\
    \texttt{-r} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
    \texttt{-R} & \textit{number} & how many times to retry transfer of every file before failing\\
    \texttt{-t} & \textit{time} & timeout in seconds (default 20)\\
    \texttt{-f} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
    \texttt{-T} && do not transfer file, just register it - destination must be non-existing meta-url\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

This command transfers contents of a file between 2 end-points.
End-points are represented by URLs or meta-URLs. For supported
endpoints please refer to Section~\ref{sec:urls}.

\texttt{arccp} can perform multi-stream transfers if \texttt{threads}
URL option is specified and server supports it.

Source URL can end with \verb#"/"#. In that case, the whole fileset
(directory) will be copied. Also, if the destination ends with
\verb#"/"#, it is extended with part of source URL after last
\verb#"/"#, thus allowing users to skip the destination file or
directory name if it is meant to be identical to the source.

\begin{framed}
   Since the job ID is in fact a \verb#gsiftp://# URL of the job
   top directory, you can use \texttt{arccp} to copy files from the
   job directory at any time.
\end{framed}

Usage examples of \texttt{arccp} are:

\begin{verbatim}
    ngcp gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535/job.out \
              file:///home/myname/job2.out
    ngcp gsiftp://aftpexp.bnl.gov;threads=10/rep/my.file \
              rc://;threads=4@grid.uio.no/lc=Collection,rc=Catalog/zebra4.f
    ngcp http://www.nordugrid.org/data/somefile gsiftp://hathi.hep.lu.se/data/
\end{verbatim}

\subsection{arcrm}\label{sec:arcrm}

The \texttt{arcrm}\footnote{In ARC $\leq$ 0.5.28 was called
  \texttt{arcremove}} \index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{ngrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    \texttt{-C} & \textit{cache\_data\_path} & store cached data\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

\begin{framed}
   A convenient use for \texttt{ngarc} is to erase the files in a data
   indexing catalog (RC, RLS or such), as it will not only remove the
   physical instance, but also will clean up the database record.
\end{framed}

Here is an \texttt{arcrm} example:

\begin{verbatim}
    ngrm rc://grid.uio.no/lc=Collection,rc=Catalog/badfile#\\
\end{verbatim}

\subsection{arcacl}\label{sec:arcacl}

\index{arcacl}\index{commands:arcacl}This command retrieves or modifies
access control information associated with a stored object if service
supports GridSite GACL language~\cite{gacl} for access control.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcacl [options] get$|$put $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{get} &\textit{URL}& get Grid ACL for the object\\
    \texttt{put} &\textit{URL}& set Grid ACL for the object\\
    \texttt{URL} && object URL; curently only gsiftp and sse URLs are supported\\
\end{longtable}

ACL document (an XML file) is printed to standard output when
\texttt{get} is requested, and is acquired from standard input when
\texttt{set} is specified\footnote{In ARC $\leq$ 0.5.28, \texttt{set}
  shoud be used instead of \texttt{put}}. Usage examples are:
\begin{verbatim}
    ngacl get gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename
    ngacl set gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename $<$ myacl
\end{verbatim}

\subsection{arctransfer}\label{sec:arctransfer}
\index{arctransfer}\index{commands:arctransfer}The \texttt{arctransfer}
This command is not implemented.