\documentclass[11pt,oneside,a4paper,english]{article}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx,epic,eepic}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{a4wide}
\usepackage{xspace}

\newcommand{\arcmigrate}{\texttt{arcmigrate}\xspace}

\begin{document}
%\maketitle
\section*{The Lunarc Application Portal - A graphical grid user interface using ARC}
The Lunarc Application Portal (LAP) is an existing web interface for
submission and management of grid jobs. As reflected in the name the
LAP is an application oriented portal, providing easy to use
interfaces for commonly available applications. The LAP is also a
framework for implementing web interfaces for user applications.

A new and updated version of LAP is presently under development which
will make use of Web 2.0 features and which will interface to the next
generation ARC client library. The latter interfacing is done in
collaboration between LAP and the KnowARC project and will allow the
KnowARC project to use the next generation LAP for it's deliverable
D2.2-2 "Advanced graphical client with easy-to-use job creation module
and support for bulk job management and monitoring".

\section*{Functionality to be offered though LAP}
Below functionality to be offered through the LAP and which will be a
part of the KnowARC deliverable D2.2-2 is listed and discussed:

\begin{itemize}
\item{The portal will support bulk job handling, i.e. it will support
  listing and sorting of (several) hundred(s) of jobs using a
  table. Using the same table bulk handling will be enabled making it
  possible to select groups of jobs to execute commands on like
  e.g. kill, clean, get, resume etc. }
\item{Job statuses will be updated automatically by a background
  processes, but a "manual update" button will also be provided.}
\item{Job "babysitting" will offer to automatically download finished
  jobs or resubmit jobs that have failed. Resubmission will be limited
  to only 2(3?) attempts. It will be possible to activate
  "babysitting" at any time for any kind of job.}
\item{Users will be able to create and maintain lists of favorite
  clusters. Blacklisting of clusters will also be possible.}
\item{The LAP is application orieented and new grid jobs are created
  through an application specific interface. The new and updated
  version of LAP will offer an application unspecific interface
  allowing users to create any kind of grid job. The interface will
  offer the user an easy to use job description creation module and
  the possibility to upload executable and job input files.}
\item{Occasionally users would like to use existing job description
  files, but still submit their grid job through the LAP. To support
  this the LAP will offer an interface for uploading and submitting
  job description files.}
\end{itemize}

\end{document}
