\chapter{Appendix}

\section{More tutorials}

Other tutorials are:\\
\\
%Oxana reported the status of OGF tutorials:
\begin{itemize}
 \item first tutorial will be given by Oxana and will deal with how to add the 
resources to Nordugrid, .... (will be related mostly to production ARC)
 \item second tutorial will be given by Gabor and he will show the 
interoperability of ARC (video demo will be shown). A-REX - Unicore 
interoperability.
 \item there will be also a tutorial related to ETICS system where the 
possibility of ETICS system to submit a job to ARC and Unicore will be 
presented. The ETICS team has not contacted so far.
\end{itemize}

Questions:
\begin{itemize}
 \item The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - Web Service   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - Web Service
 \item Does HED realises a replication Server which delegates incoming request to several threads which are communicating to the client on other free ports (I guess that not). i.e.  Front end server is running on port 60000. Request will be delegated to thread which creates a new socket on port 54305. The communication get delegated and the front end is ready for new requests.
\end{itemize}


\section{Important XSD files}
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:arched_arcecho_xml,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../../../src/hed/libs/loader/mcc.xsd}


\task{RENAMING HED configuration file into~ARC service configuration file - proposed by Marek}
\task{(echo service) client configuration file - proposed by Marek}

Link to current XSD files.

\task{Provide a list of modules to be loaded! Along with the implemented functionality which can be addressed with XML elements!!}
    mcctcp\\
\begin{verbatim}
<tcp:Listen>
	<tcp:Port>60000</tcp:Port>
	<tcp:Version>4</tcp:Version>
</tcp:Listen>
\end{verbatim}
    mcctls\\
\begin{verbatim}
 			<KeyPath>./clientKey.pem</KeyPath>
			<CertificatePath>./clientCert.pem</CertificatePath>
			<CACertificatePath>./clientCA.pem</CACertificatePath><!-- CACertificatesDir Should be /etc/... blub mention that-->

\end{verbatim}

    mcchttp\\
\begin{verbatim}
                      <next id="soap">POST</next>
                      <next id="plexer">GET</next>
                      <next id="plexer">PUT</next>
\end{verbatim}
    mccsoap\\
\begin{verbatim}
	???<ClientSSLConfig FromFile='filename'/>  
\end{verbatim}


