\chapter{Installation} 


% ** Dependencies
% *** Ordianary: log4perl and ``Redland RDF Library - Perl Interface''
% *** WebService: libperl-dev
% *** Protege: For maintaining the knowledge base


The Janitor depends on two perl packages listed in table~\ref{tab:install_dependencies}. To have the WebService interface for Janitor,
the packages listed in the table~\ref{tab:install_dependencies_optional} as build requirements.
\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for the Janitor.}{Log4perl is used for the internal logging of Janitor, while the 
                   Redland RDF libraray is used for accessing the knowledge base of RTEs.}
        \label{tab:install_dependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for Janitor.}{The library libperl-dev provides header files which are needed to link the 
                   WebService to the Perl interpreter.}
        \label{tab:install_dependencies_optional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak


If you are using regular Debian or Ubuntu packages, then the Janitor
can be installed as root by "apt-get install nordugrid-arc1-janitor".
Installing it will not drag other components of ARC with it since the
Janitor can be used in its own right or in conjunction with another
grid system, possibly. Packages for Redhat/Fedora and SuSE/OpenSuSE are
also provided, the redland library however may not yet be available for
those systems.  If you are compiling the sources yourself, the Janitor
will be enabled by default. If desired, it is possible to disable it
with the \textit{configure} flags \textit{--disable-janitor-service}
for the complete janitor or \textit{--disable-janitor-webservice} for
only the Web Service support.

Furthermore it is recommended to install the ontology editor 
Prot\`eg\`e\footnote{\href{http://protege.stanford.edu}{http://protege.stanford.edu}} in order to be to easily maintain the 
knowledge database of installable packages.







\section{Configuration}\label{sec:janitor_configuration}

The current version of Janitor can be configured using the common file \textit{arc.conf} which is to be found in the 
configuration directory \textit{etc}. Janitor is using the environment variable \textit{NORDUGRID\_CONFIG} to determine the location 
of the corresponding file. If the variable is not set, the default location \textit{/etc/arc.conf} will be used. 
The configuration is assigned by the section \lbrack janitor\rbrack. The table~\ref{tab:arc_conf_tags} contains the available tags
for janitor configuration.
\begin{landscape}
\begin{table}[!h]
   \begin{center}
        \mycaption{Tags usable in \textit{arc.conf} within the section janitor.}{Tags usable in \textit{arc.conf} within the section janitor.}
	\label{tab:arc_conf_tags}
	\begin{longtable}{|p{3cm}|p{10cm}||p{10cm}|}
	\hline
	   \textbf{tag}    & \textbf{example}                      & \textbf{description}\\
        \hline
           enabled         & "1"                                   & Boolean flag which enables or disables janitor in A-REX.\\
	   uid             & "root"                                & The effective uid. \\
	   gid             & "0"                                   & The effective gid. \\
	   registrationdir & "/var/spool/nordugrid/janitor"        & Directory where we the current states of jobs are kept. \\
	   catalog         & "/var/spool/nordugrid/janitor/catalog/knowarc.rdf"& URL of the catalog containg the package information.\\
	   downloaddir     & "/var/spool/nordugrid/janitor/download" & Directory for downloads \\
	   installationdir & "/var/spool/nordugrid/janitor/runtime"& Directory for installation of packages                   \\
	   jobexpirytime   & "7200"                                & If a job is older than this, it is considered dead and assigned to be removal pending.\\
	   rteexpirytime   & "36"                                  & If a runtime environment was not used for this time, it will be assigned to be removal pending.\\
	   allow\_base     & "*"                                   & Allow rule for base packages. \\
	   deny\_base      & "debian::etch"                        & Deny rule for base packages.\\
	   allow\_rte      & "*"                                   & Allow rule for base packages. \\
	   deny\_rte       & "APPS/MATH/ELMER-5.0.2"               & Deny rule for base packages. \\
	   logconf         & "/opt/nordugrid/etc/log.conf"         & Location of the logging configuration file for janitor.\\
	\hline
	\end{longtable}
   \end{center}
\end{table}
\end{landscape}

The parameter \texttt{enable} defines whether the Janitor shall be
used within \AREX or not. Use the value \texttt{"0"} to disable the
Janitor. The \texttt{uid} and the \texttt{gid} are defining which
effective user and group id shall be used for Janitor. Setting these to
values different from root will increase security.

The \texttt{registrationdir} describes the directory in which
the subdirectories \texttt{jobs} and \texttt{rtes} will be created.
In these directories the states of the jobs and the runtime environments
are stored. Please recall that the Janitor does not use a database as
a backend, but all communication between invocations are performed via
files in those folders.

The knowledge base of installable packages is specified by the parmeter
\texttt{catalog}.  Its value can be any kind of URL pointing to a file
written in the Resource Description Framework (RDF) format. One should
not light-heartedly use a remote address for this purpose. Such a remote
source needs to be trusted.

The specification of the RDF file will be explained in detail in
section~\ref{sec:catalog}.  The parameter \texttt{downloaddir} assignes
the directory in which the installation files will be saved after they
have been downloaded or copied from the repository which was specified by
the catalog. Please remember: the URL in arc.conf indicates the location
of the catalog. And the URLs somehow specified in the catalog specify
the location from where to download the runtime environment.

The \texttt{installationdir} finally specifies the directory into which
all packages will be installed. This \texttt{installationdir} directory
needs to be available for all computing nodes for the execution of 
arbitrary programs, mostl likely by using it as a shared NFS volume.

If the configuration file furthermore contains the \texttt{runtimedir}
tag within the section \texttt{grid-manager}, the Janitor will
also create a symbolic link in the \texttt{runtimedir} pointing to
the configuration script of the installation done by Janitor. The
tags \texttt{jobexpirytime} and \texttt{rteexpirytime} are used
for automated cleanup and are defined in seconds.  The default
value for thew\texttt{jobexpirytime} is seven days and for
the \texttt{rteexpirytime} three days.  The additional tags
\texttt{allow\_base}, \texttt{deny\_base}, \texttt{allow\_rte} and
\texttt{deny\_rte} are used to include or exclude certain base packages
or runtime environments of the catalog. This feature is useful, if the
catalog is maintain by a higher organization. But again: you need to
trust it.

The path to the log4perl configuration file is defined by the tag
\texttt{logconf}.  Examples how to configure arc and log4perl are
provided in the Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

\lstsetCONFIGURE
\begin{lstlisting}[
        label=lst:arc_conf,
        caption={ [Example \textit{arc.conf} settings for janitor.]
                  \textbf{Example \textit{arc.conf} settings for janitor.}}
        ]
[janitor]
enabled="1"
logconf="/opt/nordugrid/etc/log.conf"
registrationdir="/var/spool/nordugrid/janitor"
installationdir="/var/spool/nordugrid/janitor/runtime"
downloaddir="/var/spool/nordugrid/janitor/download"
jobexpirytime="7200"
rteexpirytime="36"
uid="root"
gid="0"
allow_base="*"
allow_rte="*"

[janitor/nordugrid]
catalog="/var/spool/nordugrid/janitor/catalog/knowarc.rdf"
\end{lstlisting}

\lstsetCONFIGURE
\begin{lstlisting}[
        label=lst:log_conf,
        caption={ [Example \textit{log.conf} settings for janitor.]
                  \textbf{Example \textit{log.conf} settings for janitor.}}
        ]
# Master Loglevel
# [OFF | DEBUG | INFO | WARN | ERROR | FATAL]
#log4perl.threshold = OFF

log4perl.rootLogger = WARN, DebugLog, MainLog, ErrorLog
log4perl.appender.DebugLog = Log::Log4perl::Appender::Screen
log4perl.appender.DebugLog.layout = PatternLayout
log4perl.appender.DebugLog.layout.ConversionPattern = [%C] %d %p> %m%n

log4perl.appender.MainLog = Log::Log4perl::Appender::File
log4perl.appender.MainLog.Threshold = DEBUG
log4perl.appender.MainLog.filename = /var/log/janitor.log
log4perl.appender.MainLog.layout = PatternLayout
log4perl.appender.MainLog.layout.ConversionPattern = %d %p> %m%n

log4perl.appender.ErrorLog = Log::Log4perl::Appender::File
log4perl.appender.ErrorLog.Threshold = ERROR
log4perl.appender.ErrorLog.filename = /var/log/janitor_error.log

log4perl.appender.ErrorLog.layout = PatternLayout
log4perl.appender.ErrorLog.layout.ConversionPattern = %d %p> %m%n
\end{lstlisting}


% ** Configuring arc.conf
% *** Where to store the data of janitor
% ** Configuring log.conf
% *** Where to store the log of janitor

\section{Limitations}

The Janitor is only available for UNIX-based servers. While not tested,
it should also be functional on MacOS X and Windows with Cygwin.

